<!--
Copyright 2015-2025 Province of British Columbia
Copyright 2021 Environment and Climate Change Canada
Copyright 2023-2025 Australian Government Department of Climate Change,
Energy, the Environment and Water

   Licensed under the Apache License, Version 2.0 (the "License");
   you may not use this file except in compliance with the License.
   You may obtain a copy of the License at

      https://www.apache.org/licenses/LICENSE-2.0

   Unless required by applicable law or agreed to in writing, software
   distributed under the License is distributed on an "AS IS" BASIS,
   WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
   See the License for the specific language governing permissions and
   limitations under the License.
-->

---
title: "ssdtools BCANZ Report"
params:
  toxicant: NA
  dists: NA
  fit_plot: NA
  gof_table: NA
  model_average_plot: NA
  pred_cl: NA
  data: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ssdtools)
library(ggplot2)
library(knitr)
library(dplyr)
library(kableExtra)
```

This report was generated through the [ssdtools Shiny app](https://bcgov-env.shinyapps.io/ssdtools)
which fits species sensitivity distributions to concentration data. 
The app is built from the R package [ssdtools](https://cran.r-project.org/web/packages/ssdtools/), and shares the same functionality.  

**Toxicant:** `r params$toxicant`   
**Report created:** `r format(Sys.Date(), "%Y-%m-%d")`    
**Input distributions:** `r params$dists`  
**ssdtools version:** `r utils::packageVersion("ssdtools")`  
**shinyssdtools version:** `r utils::packageVersion("shinyssdtools")`  
**R version:** `r gsub("R version ", "", R.version$version.string)`   

\newpage

# Fit of all distributions
```{r, message=FALSE, warning=FALSE}
params$fit_plot
```

# Goodness of fit table
```{r, message=FALSE, warning=FALSE}
kable(params$gof_table) %>%
  kable_styling(full_width = FALSE)
```

Table 1. The goodness of fit statistics.
'dist' is the distribution name; 'npars' is the number of parameters; 'nobs' is the number of observations; 'log_lik' is the log-likelihood; 'aic' is the Akaike's Information Criterion; 'aicc' is the Akaike's Information Criterion corrected for sample size; 'delta' is the Information Criterion differences; 'wt' is the Information Criterion weights; 'bic' is the Bayesian Information Criterion; 'ad' is the Anderson-Darling statistic; 'ks' is the Kolmogorov-Smirnov statistic; 'cvm' is the Cramer-von Mises statistic. 'delta' and 'wt' are based on 'aic' for censored data and 'aicc' for non-censored data. 

\newpage

# Model averaged fit
```{r, message=FALSE, warning=FALSE}
params$model_average_plot 
```

# Estimated hazardous/protective concentration
```{r, message=FALSE, warning=FALSE}
params$pred_cl |>
  kable(digits = 3) %>%
  kable_styling(full_width = FALSE)
```

Table 2. The estimated hazardous/protective concentrations. 
'HCx' is the % species affected; 'PCx' is the % species protected; 'est' is the model-averaged estimate of the concentration; 'se' is the bootstrap based standard error of the estimate; 'lcl' and 'ucl' are the bootstrapped based lower and upper 95% confidence limits; 'nboot' is the number of bootstrap samples; 'pboot' is the proportion of bootstrap samples that converged. 
The model-averaged estimate(s) is calculated by treating the distribution as a single weighted mixture distribution. 
Distributions with an absolute AIC difference greater than a default delta of 9.21 (corresponding to a weight of no more than 0.01) are excluded prior to bootstrapping.

\newpage

# Input data
```{r, message=FALSE, warning=FALSE}
kable(params$data) %>%
  kable_styling(full_width = FALSE)
```

