---
title: "ssdtools BCANZ Report"
params:
  toxicant: NA
  dists: NA
  fit_dist: NA
  fit_plot: NA
  gof_table: NA
  model_average_plot: NA
  data: NA
  nboot: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ssdtools)
library(ggplot2)
library(knitr)
library(dplyr)
```

This report was generated through the [ssdtools Shiny app](https://bcgov-env.shinyapps.io/ssdtools)
which fits species sensitivity distributions to concentration data. The app is built from the R package [ssdtools](https://cran.r-project.org/web/packages/ssdtools/), and shares the same functionality.  

**Toxicant:** `r params$toxicant`   
**Report created:** `r format(Sys.Date(), "%d/%m/%Y")`  
**Input distributions:** `r params$dists`  
**ssdtools version:** `r utils::packageVersion("ssdtools")`  
**R version:** `r gsub("R version ", "", R.version$version.string)`. 

\newpage

# Fit of all distributions
```{r, message=FALSE, warning=FALSE}
params$fit_plot
```

# Goodness of fit table
```{r, message=FALSE, warning=FALSE}
kable(params$gof_table) 
```

\newpage

# Model averaged fit
```{r, message=FALSE, warning=FALSE}
params$model_average_plot 
```

# Estimated hazard concentrations
```{r, message=FALSE, warning=FALSE}
avehc <- ssd_hc(params$fit_dist, proportion = c(0.01, 0.05, 0.1, 0.2), ci = TRUE, nboot = params$nboot, min_pboot = 0)
avehc |>
  dplyr::select(proportion, est, se, lcl, ucl, nboot, pboot) |>
  kable(digits = 3)
```

\newpage

# Data
```{r, message=FALSE, warning=FALSE}
kable(params$data)
```

